### 2022-01-08 cleave.tex
fixes vishnu

In the following we will explain the approach taken in \ac{CLEAVE} by walking the reader through the steps necessary to deploy an arbitrary \ac{NCS} emulation on top of the framework.
An overview of the structure of such an emulation on \ac{CLEAVE} can be seen in \cref{fig:cleave:ncs:struct}.

@@

\Cref{item:plant:actuators,item:plant:sensors} are in the same way provided by the user through the extension of the \texttt{Actuator} and \texttt{Sensor} abstract base classes, respectively.
\texttt{Actuator} objects process the outputs of the Controller and update the values of the \texttt{State} accordingly.
Conversely \texttt{Sensor} objects sample relevant values from the \texttt{State} object, process them, and finally pass them on to the Controller through the network.

>>>>

In the following, we will explain the approach taken in \ac{CLEAVE} by walking the reader through the steps necessary to deploy an arbitrary \ac{NCS} emulation on top of the framework.
An overview of the structure of such an emulation on \ac{CLEAVE} can be seen in \cref{fig:cleave:ncs:struct}.

@@

\Cref{item:plant:actuators,item:plant:sensors} are in the same way provided by the user through the extension of the \texttt{Actuator} and \texttt{Sensor} abstract base classes, respectively.
\texttt{Actuator} objects process the outputs of the Controller and update the values of the \texttt{State} accordingly.
Conversely, \texttt{Sensor} objects sample relevant values from the \texttt{State} object, process them, and finally pass them on to the Controller through the network.

### 2022-01-08 experiments.tex
fixes vishnu

In this section, we demonstrate the practical utility of \ac{CLEAVE} through a series of experiments on an emulated \ac{NCS} running between a client device and a cloudlet.
We aim to answer question relating to the ability of our framework to provide relevant, accurate, and repeatable measurements of the performance of \acp{NCS} deployed on edge computing infrastructure.

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_toppled}
        \caption{}%
        \label{fig:single:topple}
    \end{subfigure}%
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_rms}
        \caption{}\label{fig:single:rms}
    \end{subfigure}%
    \caption[caption]{
        Stability metrics for the single-loop scenarios.
        \labelcref{fig:single:topple} shows the fraction of plants that toppled, per experimental setup.
        \labelcref{fig:single:rms} shows the \ac{RMS} value of the angle for all penduli that did not topple in the single loop scenarios.
        Error bars indicate \SI{95}{\percent} \acp{CI}.
        }%
    \label{fig:single:stability}
\end{figure*}

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable collection and posterior processing of relevant metrics.  
\Cref{fig:single:stability} shows the results relating to the stability of the plants in the single-loop scenarios:
\cref{fig:single:topple} shows a visualization of the fraction of plants that toppled in each scenario, and \cref{fig:single:rms} shows the average \ac{RMS} amplitude for the penduli angles.
We identify toppled plants simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.

@@

\Cref{fig:video:results} shows a summary of the results obtained from the realistic scenario.
These results are interesting in their counter-intuitiveness.
Conventional wisdom would lead us to think that higher sampling rates are always better for the stability of control systems; however, \cref{fig:video:toppled,fig:video:rms} clearly shows this not to be the case for \ac{NCS} in resource-constrained scenarios.
\SI{60}{\hertz} was the least stable configuration, with at least one pendulum toppling in around \SI{16}{\percent} of the repetitions, and average pendulum angle \ac{RMS} about \num{3} times that of the \SI{40}{\hertz} scenario.
\SI{40}{\hertz} was in turn the second worst configuration --- although no penduli toppled in this scenario, average angle \ac{RMS} were double that of the \SI{20}{\hertz} setup.

We can see an explanation for these behaviors in \cref{fig:video:drop,fig:video:rtt}.
Whereas both the \SIlist{20;40}{\hertz} setups show datagram losses well below \SI{5}{\percent}, the \SI{60}{\hertz} scenario shows an average of around \SI{13}{\percent} datagrams lost.
The differences in \acp{RTT} results are equally dramatic; \acp{RTT} for the \SI{60}{\hertz} scenario were on average approximately \num{3} times those for the \SIlist{20;40}{\hertz} setups (circa \SI{41}{\milli\second} versus \SIrange[range-phrase=--]{13}{15}{\milli\second}).

These results stem from the contention for shared network resources, and hints at important trade-offs system designers will have to take into consideration when designing and developing \acl{NCS} for deployment on the edge.
The edge is envisioned as \emph{multi-tenant} and \emph{multi-instance}, and thus any edge \ac{NCS} deployment will have to be performed with shared resources in mind.
\acp{NCS} will have to dynamically adapt to system limits in order to maintain quality-of-control.

>>>>

In this section, we demonstrate the practical utility of \ac{CLEAVE} through a series of experiments on an emulated \ac{NCS} running between a client device and a cloudlet.
We aim to answer questions relating to the ability of our framework to provide relevant, accurate, and repeatable measurements of the performance of \acp{NCS} deployed on edge computing infrastructure.

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_toppled}
        \caption{}%
        \label{fig:single:topple}
    \end{subfigure}%
    \begin{subfigure}[t]{.5\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{single_loop_rms}
        \caption{}\label{fig:single:rms}
    \end{subfigure}%
    \caption[caption]{
        Stability metrics for the single-loop scenarios.
        \labelcref{fig:single:topple} shows the fraction of plants that toppled, per experimental setup.
        \labelcref{fig:single:rms} shows the \ac{RMS} value of the angle for all pendula that did not topple in the single loop scenarios.
        Error bars indicate \SI{95}{\percent} \acp{CI}.
        }%
    \label{fig:single:stability}
\end{figure*}

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable collection and posterior processing of relevant metrics.  
\Cref{fig:single:stability} shows the results relating to the stability of the plants in the single-loop scenarios:
\cref{fig:single:topple} shows a visualization of the fraction of plants that toppled in each scenario, and \cref{fig:single:rms} shows the average \ac{RMS} amplitude for the pendula angles.
We identify toppled plants simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.

@@

\Cref{fig:video:results} shows a summary of the results obtained from the realistic scenario.
These results are interesting in their counter-intuitiveness.
Conventional wisdom would lead us to think that higher sampling rates are always better for the stability of control systems; however, \cref{fig:video:toppled,fig:video:rms} clearly shows this not to be the case for \ac{NCS} in resource-constrained scenarios.
\SI{60}{\hertz} was the least stable configuration, with at least one pendulum toppling in around \SI{16}{\percent} of the repetitions, and average pendulum angle \ac{RMS} about \num{3} times that of the \SI{40}{\hertz} scenario.
\SI{40}{\hertz} was in turn the second worst configuration --- although no pendula toppled in this scenario, average angle \ac{RMS} were double that of the \SI{20}{\hertz} setup.

We can see an explanation for these behaviors in \cref{fig:video:drop,fig:video:rtt}.
Whereas both the \SIlist{20;40}{\hertz} setups show datagram losses well below \SI{5}{\percent}, the \SI{60}{\hertz} scenario shows an average of around \SI{13}{\percent} of datagrams lost.
The differences in \acp{RTT} results are equally dramatic; \acp{RTT} for the \SI{60}{\hertz} scenario were on average approximately \num{3} times those for the \SIlist{20;40}{\hertz} setups (circa \SI{41}{\milli\second} versus \SIrange[range-phrase=--]{13}{15}{\milli\second}).

These results stem from the contention for shared network resources, and hints at important trade-offs system designers will have to take into consideration when designing and developing \acl{NCS} for deployment on the edge.
The edge is envisioned as \emph{multi-tenant} and \emph{multi-instance}, and thus any edge \ac{NCS} deployment will have to be performed with shared resources in mind.
\acp{NCS} will have to dynamically adapt to system limits in order to maintain quality of control.

### 2022-01-08 intro.tex
fixes vishnu

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2009Case,Satya2017Emergence}, comsumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

>>>>

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2009Case,Satya2017Emergence}, consumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.
